Learning and comparing functional connectomes between populations

### 2012-12-29 paper.tex
iter on intro

Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
challenges.

>>>>

Brain functional connectivity captures the synchronization of distant
neural systems via correlations in brain activity. Given that brain
function emerges from the interaction of specialized units, functional
connectivity is an essential part of the description of brain function,
complementary to the localizationist picture emerging from the systematic
mapping of regions recruited in tasks. However, while activation mapping
has a well-defined standard analysis framework that enables
statistically-controlled comparisons across subjects \cite{friston1995},
group-level analysis of functional connectivity is still offers many
methodological challenges. Giving a picture of functional connectivity at
the subject level is by itself not straightforward, as the brain
comprises a myriad of interacting subsystems and must be decomposed in
simplified and synthetic representations: distributed functional networks
depicted by their spatial maps \cite{fox2005} or a connections linking
localized functional modules depicted as a graph \cite{bullmore2009}.
Here we focus on the latter: the functional connectome \cite{sporns2005}.
